Creating optimal conditions for reproducible data analysis in R with `fertile`

### 2020-02-23 fertile.Rmd
more bibliography updates

bibliography: bibliography.bib
output: rticles::asa_article
---

@@

There appear to be no existing tools that cater to analysts looking for an easy-to-learn, easy-to-implement, fast way to obtain a broad overview of their projects' reproducibility.
To address this, we present an R package called [**fertile**](https://github.com/baumer-lab/fertile) [^1]:{The authors gratefully acknowledge contributions from Hadley Wickham, Jenny Bryan, Greg Wilson, Edgar Ruiz, and other members of the `tidyverse` team.}, a low barrier-to-entry package which focuses on a series of common mistakes programmers make while conducting data science research in R.

@@

Much of the available literature focuses on file structure, organization, and naming, and **fertile`**s features are consistent with this. The *ideal* file structure is not agreed upon by academics, though there are some recommendations focused on R that are available. @marwick2018packaging provides the framework for file structure that **fertile** is based on: a structure similar to that of an R package, with an `R` folder, as well as `data`, `data-raw`, `inst` and `vignettes`.

@@

rrtools
• Complementary to Ben Marwick's paper
• Creates a basic R package structure for your research and institutes some testthat check functionality

@@

```{r, eval = FALSE, include = FALSE}
knitr::write_bib("dplyr", file = "pkgs.bib")
```

>>>>

bibliography: [bibliography.bib, pkgs.bib]
output: rticles::asa_article
---

```{r, include = FALSE}
knitr::write_bib(c("dplyr", "rrtools", "tidyverse", "orderly", "workflowr", "testthat"),  file = "pkgs.bib")
```

@@

There appear to be no existing tools that cater to analysts looking for an easy-to-learn, easy-to-implement, fast way to obtain a broad overview of their projects' reproducibility.
To address this, we present an R package called [**fertile**](https://github.com/baumer-lab/fertile) [^1].

[^1]:{The authors gratefully acknowledge contributions from Hadley Wickham, Jenny Bryan, Greg Wilson, Edgar Ruiz, and other members of the **tidyverse** team.}, a low barrier-to-entry package which focuses on a series of common mistakes programmers make while conducting data science research in R.

@@

Much of the available literature focuses on file structure, organization, and 
naming, and **fertile**s features are consistent with this. The *ideal* file 
structure is not agreed upon by academics, though there are some recommendations 
focused on R that are available. @marwick2018packaging provides the framework for 
file structure that **fertile** is based on: a structure similar to that of an R 
package, with an `R` folder, as well as `data`, `data-raw`, `inst` and `vignettes`.

@@

There also exists a small selection of R packages that work to address the issue of research reproducibility, though not all of them are available on `CRAN`. **rrtools** [@R-rrtools], developed to address some of the issues discussed in @marwick2018packaging, creates a basic R package structure for a data analysis project and implements a basic **testthat** `check` functionality.

@@
